Parity games in pushdown systems with parameters

### 2023-06-20 reachability/article.tex
up

{\bf Extensions of  pushdown automata/systems ?}
Extensions of pushdown systems with storage for later comparisons
have been introduced for instance as register pushdown systems. 
Such automata possess registers in addition to their stack, and can keep data values in both.
Register pushdown systems have been shown to have applications for malware detection and XML schema checking \cite{senda2021forward, senda2021ltl}. 
In theory, since registers can be unfilled and later be filled again an unbounded number of times, the number of different data values a pushdown register systems can store in its registers in a run is unbounded.  
In \cite{murawski2017reachability} it was shown however that a register pushdown automaton can
only really ``remember'' at most  $3r$ data values, where $r$ is the number of registers,
% Even though pushdown register systems have no bound on the number of elements of the alphabet that they can store at any instant, over the course of a run they can really “remember” at most 3r of them, 
i.e. for any run of a register pushdown automaton with $r$ registers there exists an equivalent run %, i.e.
 with the same initial and final conﬁgurations, but in which every configuration contains register assignments drawn from only $3r$ elements. This 
 %can 
 leads to
 the
  question
  of
   how useful the ability to unfill and later refill registers really is compared to a model that would only specify valuations once.

>>>>

{\bf Related models.}
Extensions of pushdown systems with storage for later comparisons
have been introduced for instance as register pushdown systems. 
Such automata possess registers in addition to their stack, and can keep data values in both.
Register pushdown systems have been shown to have applications for malware detection and XML schema checking \cite{senda2021forward, senda2021ltl}. 
In theory, since registers can be unfilled and later be filled again an unbounded number of times, the number of different data values a pushdown register systems can store in its registers in a run is unbounded.  
In \cite{murawski2017reachability} it was shown however that a register pushdown automaton can
only really ``remember'' at most  $3r$ data values, where $r$ is the number of registers,
% Even though pushdown register systems have no bound on the number of elements of the alphabet that they can store at any instant, over the course of a run they can really “remember” at most 3r of them, 
i.e. for any run of a register pushdown automaton with $r$ registers there exists an equivalent run %, i.e.
 with the same initial and final conﬁgurations, but in which every configuration contains register assignments drawn from only $3r$ elements. This 
 %can 
 leads to
 the
  question
  of
   how useful the ability to unfill and later refill registers really is compared to a model that would only specify valuations once.
